---
title: "Salamander_data"
format: html
editor: visual
messages: FALSE
warnings: FALSE
---

```{r}
library(tidyverse)
library(janitor)
library(dplyr)
mack_verts <- read_csv(here("data","AS00601.csv"))

mack_verts
```

```{r}
names(mack_verts)
```

```{r}
names(mack_verts) <- tolower(names(mack_verts))
names(mack_verts)
```
```{r}
#Storing 5th values in column  "Weight" as mc_wt_5

mc_wt_5 <- mack_verts[5,15]
mc_wt_5
```
# Store the 8th - 20th value in the “LENGTH1” column as mc_length_8_20. Check by looking at your data frame to confirm.
 
```{r}
mc_length_8_20 <- mack_verts[8:20, 13]
mc_length_8_20

```

```{r}
mc_dates <- mack_verts[,17]
mc_dates
```

# Create a subset that only contains observations for Pacific Giant Salamanders (species Dicamptodon tenebrosus, stored in species as DITE). Store the subset as mc_salamanders. Hint: see dplyr::filter()!


```{r}
mc_salamaders <- mack_verts %>%
  dplyr::filter(species == "DITE")
mc_salamaders
```


```{r}

ggplot(data = mc_salamaders, aes( x = length1, y = weight)) + geom_jitter() + 
  geom_point(
    colour = 'red', size = 1) + 
  labs(x = "Salamander Weigth", 
       y = "Salamander Length",
       title = "Weight and Length Correlation",
       subtitle = "Slamander Weight vs Legth",
       caption = "Source is Salamander Dataset") + theme_dark()
  )
  
  
```

#making a cutthroat plot

Similar to above, make a subset called mc_trout that only contains observations for cutthroat trout (species “ONCL”)

```{r}
mc_trout <- mack_verts |>
  filter(species == "ONCL")
mc_trout
```

Create a scatterplot of length1 by weight for all trout in the dataset
#CHECKING REACH
```{r}
unique(mc_trout$reach)
```


```{r}

custom_colors <- c("L" = "red", "U"= "blue", "M"= "forestgreen")

cutthroat_plot <-
ggplot(data = mc_trout, aes(x = length1, y = weight)) + 
  geom_point(aes(color = reach)) +
  scale_color_manual(values = custom_colors) + #assign custom colors
  facet_wrap(~reach) +
  theme_minimal()
cutthroat_plot
```

Customize so that the point color depends on reach
Customize your color scheme (e.g. scale_color_manual())
Facet your plot by creek reach (hint: facet_wrap(~...))
Update graph axis labels and title
Export your graph as cutthroat_size.png to the figs folder

```{r}
#ggsave(plot = cutthroat_plot, here::here("figs", "cutthroat_plot.png"))
```



